Phylodynamic inference of contact network parameters through approximate Bayesian computation

### 2016-06-01 doc/thesis/methods_results.Rnw
moved objective stuff to methods and expanded

@@

\uline{To analyse the effects of the true parameter values on the
accuracy our estimates of \gls{alpha} and \gls{I}, we fitted one \glspl{GLM}
for each of these two parameters, with error rate as the dependent variable and
the true parameter values as independent variables. Since the estimates of
\gls{m} and \gls{N} were roughly equal across all simulations}
(\cref{fig:abcptm2,fig:abcptm3,fig:abcptm4}), \uline{\glspl{GLM} were not
fitted for these parameters. The estimated coefficients are shown in
}\cref{tab:glmalpha,tab:glmI}. \uline{For the parameters \gls{alpha}, \gls{I},
and \gls{N}, the \gls{GLM} were fitted using the inverse link function. That
is, if $p$ is the true value of the parameter and $\hat{p}$ is a random
variable representing our estimate of the parameter, the \gls{GLM} posits a
relationship of the form }
\[
    \E(|p-\hat{p}|) = (\beta_0 + \beta_\alpha \alpha + \beta_I I + \beta_m m)^{-1},
\]
\uline{where the $\beta$'s are coefficients to be fitted. If the true value
\gls{alpha}, say, is increased by one, the \emph{inverse} of the expected
absolute error will increase by $\beta_\alpha$. If $\beta_\alpha$ is positive,
it means that the absolute error decreases as the true value of \gls{alpha}
increases.}

@@

\uline{The \gls{GLM} analysis indicated that the error in estimates of
\gls{alpha} decreased with larger true values of \gls{alpha} 
    ($p \Sexpr{pp(alpha.glm[Parameter == "alpha", p], eq=TRUE)}$)
and \gls{m}
    ($p \Sexpr{pp(alpha.glm[Parameter == "m", p], eq=TRUE)}$)
but was not significatly affected by \gls{I}} (\cref{tab:glmalpha}). 
\uline{Qualitatively, \gls{alpha} seemed to be only weakly identifiable between
the values of 0 and 0.5} (\cref{fig:abcptm2}). \uline{The error in the
estimated prevalence \gls{I} was slightly lower for smaller values of
\gls{alpha}
    ($p \Sexpr{pp(I.glm[Parameter == "alpha", p], eq=TRUE)}$)
and \gls{I}
    ($p \Sexpr{pp(I.glm[Parameter == "I", p], eq=TRUE)}$),
but was not significantly affected by the true value of \gls{m}} 
(\cref{tab:glmI}).}

>>>>

\subsection{Justification for approach}
\label{subsec:just}

{\color{blue}\uline{We present here a non-rigorous justification for the use of
\gls{ABC} for the problem at hand, as opposed to more frequently-used
approaches for fitting mathematical models} (see \cref{chp:prelim}).
\uline{Consider a contact network model with parameters $\theta$, and an
estimated transmission tree $T$. Taking a Bayesian approach, our aim is to
obtain a sample from the posterior distribution on the model's parameters given
our data,}
\[
    \Pr(\theta \mid T) = \frac{\Pr(T \mid \theta) \Pr(\theta)}{\Pr(T)}.
\]
\uline{For all but the simplest models, the normalizing constant $\Pr(T)$ is an
intractable integral. What we shall argue here is that, in contrast to most
commonly studied mathematical models, the likelihood $\Pr(T \mid \theta)$ is
also likely to be intractible in our case.}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{transtree}
    \caption[
        Illustration of an estimated transmission tree without labels and two
        possible underlying complete transmission trees with labels.
    ]{
        Illustration of an estimated transmission tree without labels (left)
        and two possible underlying complete transmission trees with labels
        (right). In the top right scenario, the epidemic began with node $a$
        who transmitted first to $b$ and then to $c$. In the bottom right
        scenario, $b$ was the index case; $b$ infected $c$, who went on to
        infect $a$. A transmission tree estimated from a viral phylogeny would
        have the same topology and tip labels in both cases.
    }
    \label{fig:tt}
\end{figure}

\uline{As discussed in} \cref{subsec:tt}, \uline{the internal nodes of
transmission trees represent transmission events, and are labelled with the
donor in the associated transmission pair. However, when we estimate a
transmission tree from viral sequence data, we generally only know the labels
of the tips of the tree, not the labels of the internal nodes. In viral
phylogenies, the transmissions are at least partially preserved through the
evolutionary relationships among the viruses, but the directionality of those
transmissions is unknown. Thus, a single estimated transmission tree can
correspond to many possible pathways of the epidemic through the network.
}\Cref{fig:tt} \uline{illustrates this concept for a simple transmission tree
with three tips. When calculating a likelihood given a transmission tree, we
must sum over all possible labellings of the internal nodes. Let $\Nu$ be the
set of such labellings. Then}
\begin{align}
    \Pr(T \mid \theta) = \sum{\nu \in \Nu} \Pr(T, \nu \mid \theta).
    \label{eq:lik1}
\end{align}
\uline{A contact network model assigns a probability to each possible contact
network. Transmission trees are realized over particular contact networks, not
over the model itself. Therefore, we must also sum over all contact networks
which could be generated by the model. Let $\G$ be the set of all possible
contact networks. Summing } \cref{eq:lik1} \uline{over $\G$ gives}
\begin{align}
    \Pr(T \mid \theta) = \sum_{G \in \G} \sum{\nu \in \Nu} 
        \Pr(T, \nu \mid G, \theta) \Pr(G \mid \theta).
    \label{eq:lik2}
\end{align}
\uline{This can be simplified somewhat by noticing that, given a specific
contact network, the labelled transmission tree depends only on that network
and not on the model that generated it. That is, $\Pr(T, \nu \mid G, \theta) =
\Pr(T, \nu \mid G)$, and}
\begin{align}
    \Pr(T \mid \theta) = \sum_{G \in \G} \Pr(G \mid \theta) \sum{\nu \in \Nu} 
        \Pr(T, \nu \mid G)
    \label{eq:lik3}
\end{align}
\uline{Under the assumption that both transmission and removal are Poisson
processes, calculating $\Pr(T, \nu \mid G)$ can be accomplished by a
straightforward modification of the Gillespie simulation algorithm} 
(\cref{alg:nettree}). \uline{Rather than choosing transmission or removal
events according to their probabilities, the events would be deterministically
chosen based on the transmission tree and the probabilities of each event
would be multiplied together. Assuming efficient data structures for storing
lists of nodes and edges, the complexity of this calculation would be $O(|T|)$.
The number of possible labellings of internal nodes of $T$ is easily seen to be
$2^{(|T|-1)/2}$ by noticing that each of the $(|T|-1)/2$ internal nodes must be
labelled with the same label as either its right child or its left child.
Although exponential calculations of this nature can are often be simplified on 
trees using dynamic programming} (\eg \autocite{pupko2000fast}), \uline{it
cannot be straightforwardly applied in this case because the subtrees'
probabilities depend on the existing epidemic progress (their parents and
siblings). Hence, calculating the inner sum over labels may take time
$O(2^{(|T|-1)/2})$.}

\uline{The outer sum, over all contact networks, is also difficult to evaluate
in general. There are $2^{N(N-1)}$ directed graphs on $N$
nodes~\autocite{harary2014graphical}. There must be at least as many nodes in
the contact network as the number of tips in the tree, which is $(|T|+1)/2$. Of
course, it is very likely that there are more nodes in the network than
observed tips because some individuals are never infected and/or some infected
individuals are never sampled. The complexity of calculating $\Pr(G \mid
\theta)$ is obviously dependent on the particular model being investigated. For
the \gls{BA} model, we might have to sum over all possible orders in which the
nodes could be added, and all assignments of edges to the nodes which generated
them. However, even in the unlikely case that calculating $\Pr(G \mid \theta)$
can be done in constant time, the sum} \ref{eq:lik3} \uline{still has at least
$O(2^{|T|^2})$ terms.}

\uline{We have shown that both the normalizing constant $\Pr(T)$ and the
likelihood $\Pr(T \mid \theta)$ are likely computationally prohibitive to
calculate. If this is the case, the problem of fitting contact network models
to phylogenies seems to be of the \emph{doubly-intractible}
type~\autocite{murray2012mcmc}, which would imply that these models are not
amenable to neither \gls{ML} nor Bayesian inference techniques. Although both
methods are able to cope with an intractible normalizing constant (for example,
by local search for \gls{ML} or Bayesian \gls{MCMC}), neither can avoid the
intractable likelihood calculations. This justifies the use of \gls{ABC}, which
is a likelihood-free method.}

\uline{We have not proven here that} \cref{eq:lik3} \uline{is impossible to
calculate in polynomial time - it could be possible to algebraically simplify
the sum into a tractable expression. Furthermore, under certain models, a large
proportion of $\G$ may have zero probability, which would enable the
simplification of the outer sum on a model-specific basis. It should also be
noted that extensions of Bayesian \gls{MCMC} have been developed for
doubly-intractable problems~\autocite{liang2010double, murray2012mcmc}, which
might be adaptable to the problem at hand. These have not been as widely used
as \gls{ABC}, nor are they as easily parallelizable as \gls{SMC}. }}

@@

\uline{To analyse the effects of the true parameter values on the
accuracy our estimates of \gls{alpha} and \gls{I}, we fitted one \glspl{GLM}
for each of these two parameters, with error rate as the dependent variable and
the true parameter values as independent variables. Since the estimates of
\gls{m} and \gls{N} were roughly equal across all simulations}
(\cref{fig:abcptm2,fig:abcptm3,fig:abcptm4}), \uline{\glspl{GLM} were not
fitted for these parameters. The estimated coefficients are shown in
}\cref{tab:glmalpha,tab:glmI}. \uline{For the parameters \gls{alpha}, \gls{I},
and \gls{N}, the \gls{GLM} were fitted using the inverse link function. That
is, if $p$ is the true value of the parameter and $\hat{p}$ is a random
variable representing our estimate of the parameter, the \gls{GLM} posits a
relationship of the form }
\[
    \E(|p-\hat{p}|) = (\beta_0 + \beta_\alpha \alpha + \beta_I I + \beta_m m)^{-1},
\]
\uline{where the $\beta$'s are coefficients to be fitted. If the true value
\gls{alpha}, say, is increased by one, the \emph{inverse} of the expected
absolute error will increase by $\beta_\alpha$. If $\beta_\alpha$ is positive,
it means that the absolute error decreases as the true value of \gls{alpha}
increases.}}

@@

<<glm_tables, echo=FALSE, warning=FALSE, error=FALSE, results="asis">>=
    source("global.R")
    format.glm <- function (df) {
        df.copy <- copy(df)
        df.copy[Parameter == "alpha", Parameter := "$\\alpha$"]
        df.copy[,p := paste0("$", sapply(p, pp, eq=FALSE), "$")]
        df.copy[,Estimate := paste0("$", sapply(Estimate, pp, eq=FALSE, thres=NA), "$")]
        df.copy[,`Standard error` := paste0("$", sapply(`Standard error`, pp, eq=FALSE, thres=NA), "$")]
        setnames(df.copy, "p", "$p$-value")
        df.copy
    }

    alpha.glm.tbl <- format.glm(alpha.glm)
    I.glm.tbl <- format.glm(I.glm)

    capt.short <- paste("Parameters of a fitted GLM relating error in estimated",
                        "$\\alpha$ to true values of BA parameters.")
    capt <- paste(capt.short, "GLM was fitted with a Gaussian distribution and",
                  "inverse link function. Coefficients are interpretable as",
                  "additive effects on the inverse of the mean error.")
    print(xtable(alpha.glm.tbl, label="tab:glmalpha", caption=c(capt, capt.short)),
          include.rownames=FALSE, sanitize.text.function=identity,
          sanitize.colnames.function=identity)

    capt.short <- paste("Parameters of a fitted GLM relating error in estimated",
                        "$I$ to true values of BA parameters.")
    capt <- paste(capt.short, "GLM was fitted with a gaussian distribution and",
                  "inverse link function. Coefficients are interpretable as",
                  "additive effects on the inverse of the mean error.")
    print(xtable(I.glm.tbl, label="tab:glmI", caption=c(capt, capt.short)),
          include.rownames=FALSE, sanitize.text.function=identity,
          sanitize.colnames.function=identity)
@

{\color{blue}\uline{The \gls{GLM} analysis indicated that the error in estimates of
\gls{alpha} decreased with larger true values of \gls{alpha} 
    ($p \Sexpr{pp(alpha.glm[Parameter == "alpha", p], eq=TRUE)}$)
and \gls{m}
    ($p \Sexpr{pp(alpha.glm[Parameter == "m", p], eq=TRUE)}$)
but was not significatly affected by \gls{I}} (\cref{tab:glmalpha}). 
\uline{Qualitatively, \gls{alpha} seemed to be only weakly identifiable between
the values of 0 and 0.5} (\cref{fig:abcptm2}). \uline{The error in the
estimated prevalence \gls{I} was slightly lower for smaller values of
\gls{alpha}
    ($p \Sexpr{pp(I.glm[Parameter == "alpha", p], eq=TRUE)}$)
and \gls{I}
    ($p \Sexpr{pp(I.glm[Parameter == "I", p], eq=TRUE)}$),
but was not significantly affected by the true value of \gls{m}} 
(\cref{tab:glmI}).}

### 2016-06-01 doc/thesis/methods_results.tex
moved objective stuff to methods and expanded

@@

\uline{To analyse the effects of the true parameter values on the
accuracy our estimates of \gls{alpha} and \gls{I}, we fitted one \glspl{GLM}
for each of these two parameters, with error rate as the dependent variable and
the true parameter values as independent variables. Since the estimates of
\gls{m} and \gls{N} were roughly equal across all simulations}
(\cref{fig:abcptm2,fig:abcptm3,fig:abcptm4}), \uline{\glspl{GLM} were not
fitted for these parameters. The estimated coefficients are shown in
}\cref{tab:glmalpha,tab:glmI}. \uline{For the parameters \gls{alpha}, \gls{I},
and \gls{N}, the \gls{GLM} were fitted using the inverse link function. That
is, if $p$ is the true value of the parameter and $\hat{p}$ is a random
variable representing our estimate of the parameter, the \gls{GLM} posits a
relationship of the form }
\[
    \E(|p-\hat{p}|) = (\beta_0 + \beta_\alpha \alpha + \beta_I I + \beta_m m)^{-1},
\]
\uline{where the $\beta$'s are coefficients to be fitted. If the true value
\gls{alpha}, say, is increased by one, the \emph{inverse} of the expected
absolute error will increase by $\beta_\alpha$. If $\beta_\alpha$ is positive,
it means that the absolute error decreases as the true value of \gls{alpha}
increases.}

\uline{The \gls{GLM} analysis indicated that the error in estimates of
\gls{alpha} decreased with larger true values of \gls{alpha} 
    ($p {<}10^{-5}$)
and \gls{m}
    ($p =0.01$)
but was not significatly affected by \gls{I}} (\cref{tab:glmalpha}). 
\uline{Qualitatively, \gls{alpha} seemed to be only weakly identifiable between
the values of 0 and 0.5} (\cref{fig:abcptm2}). \uline{The error in the
estimated prevalence \gls{I} was slightly lower for smaller values of
\gls{alpha}
    ($p {<}10^{-5}$)
and \gls{I}
    ($p =0.05$),
but was not significantly affected by the true value of \gls{m}} 
(\cref{tab:glmI}).}

@@

%To test the effect of model misspecification, we simulated one network where
%the nodes exhibited heterogeneous preferential attachment power (half 0.5, the
%other half 1.5), with $m$ = 2, $N$ = 5000, and $I$ = 1000. The MAP [95\%
%HPD] estimates for each parameter were: 
%$\alpha$, 
%  round(d["alpha", map], 2) 
%  [round(d["alpha", hpd.min], 2) -
%   round(d["alpha", hpd.max], 2)];
%$I$,
%  d["I", round(map)] 
%  [d["I", round(hpd.min)] -
%   d["I", round(hpd.max)]];
%$m$,
%  d["m", floor(map)] 
%  [d["m", floor(hpd.min)] -
%   d["m", floor(hpd.max)]];
%$N$,
%  d["N", round(map)] 
%  [d["N", round(hpd.min)] -
%   d["N", round(hpd.max)]].
%The approximate posterior distributions for this simulation are shown in
%\cref{fig:mixed}. To test the effect of sampling bias, we sampled one
%transmission tree in a peer-driven fashion, where the probability to sample a
%node was twice as high if one of its peers had already been sampled. The
%parameters for this experiment were $N$ = 5000, $m$ = 2, $\alpha$ = 0.5, and
%$I$ = 2000. The estimated values were
%$\alpha$, 
%  p["alpha", round(map, 2)] 
%  [p["alpha", round(hpd.min, 2)] -
%   p["alpha", round(hpd.max, 2)]];
%$I$,
%  p["I", floor(map)] 
%  [p["I", floor(hpd.min)] -
%   p["I", floor(hpd.max)]];
%$m$,
%  p["m", floor(map)] 
%  [p["m", floor(hpd.min)] -
%   p["m", floor(hpd.max)]];
%$N$,
%  p["N", floor(map)] 
%  [p["N", floor(hpd.min)] -
%   p["N", floor(hpd.max)]].
%The approximate posterior distributions are shown in \cref{fig:peerdriven}. Both
%of these results were in line with estimates obtained on other simulated
%datasets (\cref{tab:abchpd}), although the estimate of peer-driven sampling for
%$\alpha$ was somewhat lower than typical.

%\subsubsection*{Effect of parameters on power-law exponent}
%
%\Cref{tab:glm} shows the estimated parameters for a log-link \gls{GLM} fitted
%to the observed distribution of \gls{gamma} values. The coefficients are
%interpretable as multiplicative effects.
%
%\begin{table}
%    \centering
%    \input{\tablepath/pa-gamma-glm}
%    \caption{Estimated \gls{GLM} parameters for relationship between power-law
%    exponent \gls{gamma} and \gls{BA} model parameters.}
%    \label{tab:glm}
%\end{table}

>>>>

\subsection{Justification for approach}
\label{subsec:just}

{\color{blue}\uline{We present here a non-rigorous justification for the use of
\gls{ABC} for the problem at hand, as opposed to more frequently-used
approaches for fitting mathematical models} (see \cref{chp:prelim}).
\uline{Consider a contact network model with parameters $\theta$, and an
estimated transmission tree $T$. Taking a Bayesian approach, our aim is to
obtain a sample from the posterior distribution on the model's parameters given
our data,}
\[
    \Pr(\theta \mid T) = \frac{\Pr(T \mid \theta) \Pr(\theta)}{\Pr(T)}.
\]
\uline{For all but the simplest models, the normalizing constant $\Pr(T)$ is an
intractable integral. What we shall argue here is that, in contrast to most
commonly studied mathematical models, the likelihood $\Pr(T \mid \theta)$ is
also likely to be intractible in our case.}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{transtree}
    \caption[
        Illustration of an estimated transmission tree without labels and two
        possible underlying complete transmission trees with labels.
    ]{
        Illustration of an estimated transmission tree without labels (left)
        and two possible underlying complete transmission trees with labels
        (right). In the top right scenario, the epidemic began with node $a$
        who transmitted first to $b$ and then to $c$. In the bottom right
        scenario, $b$ was the index case; $b$ infected $c$, who went on to
        infect $a$. A transmission tree estimated from a viral phylogeny would
        have the same topology and tip labels in both cases.
    }
    \label{fig:tt}
\end{figure}

\uline{As discussed in} \cref{subsec:tt}, \uline{the internal nodes of
transmission trees represent transmission events, and are labelled with the
donor in the associated transmission pair. However, when we estimate a
transmission tree from viral sequence data, we generally only know the labels
of the tips of the tree, not the labels of the internal nodes. In viral
phylogenies, the transmissions are at least partially preserved through the
evolutionary relationships among the viruses, but the directionality of those
transmissions is unknown. Thus, a single estimated transmission tree can
correspond to many possible pathways of the epidemic through the network.
}\Cref{fig:tt} \uline{illustrates this concept for a simple transmission tree
with three tips. When calculating a likelihood given a transmission tree, we
must sum over all possible labellings of the internal nodes. Let $\Nu$ be the
set of such labellings. Then}
\begin{align}
    \Pr(T \mid \theta) = \sum{\nu \in \Nu} \Pr(T, \nu \mid \theta).
    \label{eq:lik1}
\end{align}
\uline{A contact network model assigns a probability to each possible contact
network. Transmission trees are realized over particular contact networks, not
over the model itself. Therefore, we must also sum over all contact networks
which could be generated by the model. Let $\G$ be the set of all possible
contact networks. Summing } \cref{eq:lik1} \uline{over $\G$ gives}
\begin{align}
    \Pr(T \mid \theta) = \sum_{G \in \G} \sum{\nu \in \Nu} 
        \Pr(T, \nu \mid G, \theta) \Pr(G \mid \theta).
    \label{eq:lik2}
\end{align}
\uline{This can be simplified somewhat by noticing that, given a specific
contact network, the labelled transmission tree depends only on that network
and not on the model that generated it. That is, $\Pr(T, \nu \mid G, \theta) =
\Pr(T, \nu \mid G)$, and}
\begin{align}
    \Pr(T \mid \theta) = \sum_{G \in \G} \Pr(G \mid \theta) \sum{\nu \in \Nu} 
        \Pr(T, \nu \mid G)
    \label{eq:lik3}
\end{align}
\uline{Under the assumption that both transmission and removal are Poisson
processes, calculating $\Pr(T, \nu \mid G)$ can be accomplished by a
straightforward modification of the Gillespie simulation algorithm} 
(\cref{alg:nettree}). \uline{Rather than choosing transmission or removal
events according to their probabilities, the events would be deterministically
chosen based on the transmission tree and the probabilities of each event
would be multiplied together. Assuming efficient data structures for storing
lists of nodes and edges, the complexity of this calculation would be $O(|T|)$.
The number of possible labellings of internal nodes of $T$ is easily seen to be
$2^{(|T|-1)/2}$ by noticing that each of the $(|T|-1)/2$ internal nodes must be
labelled with the same label as either its right child or its left child.
Although exponential calculations of this nature can are often be simplified on 
trees using dynamic programming} (\eg \autocite{pupko2000fast}), \uline{it
cannot be straightforwardly applied in this case because the subtrees'
probabilities depend on the existing epidemic progress (their parents and
siblings). Hence, calculating the inner sum over labels may take time
$O(2^{(|T|-1)/2})$.}

\uline{The outer sum, over all contact networks, is also difficult to evaluate
in general. There are $2^{N(N-1)}$ directed graphs on $N$
nodes~\autocite{harary2014graphical}. There must be at least as many nodes in
the contact network as the number of tips in the tree, which is $(|T|+1)/2$. Of
course, it is very likely that there are more nodes in the network than
observed tips because some individuals are never infected and/or some infected
individuals are never sampled. The complexity of calculating $\Pr(G \mid
\theta)$ is obviously dependent on the particular model being investigated. For
the \gls{BA} model, we might have to sum over all possible orders in which the
nodes could be added, and all assignments of edges to the nodes which generated
them. However, even in the unlikely case that calculating $\Pr(G \mid \theta)$
can be done in constant time, the sum} \ref{eq:lik3} \uline{still has at least
$O(2^{|T|^2})$ terms.}

\uline{We have shown that both the normalizing constant $\Pr(T)$ and the
likelihood $\Pr(T \mid \theta)$ are likely computationally prohibitive to
calculate. If this is the case, the problem of fitting contact network models
to phylogenies seems to be of the \emph{doubly-intractible}
type~\autocite{murray2012mcmc}, which would imply that these models are not
amenable to neither \gls{ML} nor Bayesian inference techniques. Although both
methods are able to cope with an intractible normalizing constant (for example,
by local search for \gls{ML} or Bayesian \gls{MCMC}), neither can avoid the
intractable likelihood calculations. This justifies the use of \gls{ABC}, which
is a likelihood-free method.}

\uline{We have not proven here that} \cref{eq:lik3} \uline{is impossible to
calculate in polynomial time - it could be possible to algebraically simplify
the sum into a tractable expression. Furthermore, under certain models, a large
proportion of $\G$ may have zero probability, which would enable the
simplification of the outer sum on a model-specific basis. It should also be
noted that extensions of Bayesian \gls{MCMC} have been developed for
doubly-intractable problems~\autocite{lang2010double, murray2012mcmc}, which
might be adaptable to the problem at hand. These have not been as widely used
as \gls{ABC}, nor as easily parallelizable as \gls{SMC}. }}

@@

\uline{To analyse the effects of the true parameter values on the
accuracy our estimates of \gls{alpha} and \gls{I}, we fitted one \glspl{GLM}
for each of these two parameters, with error rate as the dependent variable and
the true parameter values as independent variables. Since the estimates of
\gls{m} and \gls{N} were roughly equal across all simulations}
(\cref{fig:abcptm2,fig:abcptm3,fig:abcptm4}), \uline{\glspl{GLM} were not
fitted for these parameters. The estimated coefficients are shown in
}\cref{tab:glmalpha,tab:glmI}. \uline{For the parameters \gls{alpha}, \gls{I},
and \gls{N}, the \gls{GLM} were fitted using the inverse link function. That
is, if $p$ is the true value of the parameter and $\hat{p}$ is a random
variable representing our estimate of the parameter, the \gls{GLM} posits a
relationship of the form }
\[
    \E(|p-\hat{p}|) = (\beta_0 + \beta_\alpha \alpha + \beta_I I + \beta_m m)^{-1},
\]
\uline{where the $\beta$'s are coefficients to be fitted. If the true value
\gls{alpha}, say, is increased by one, the \emph{inverse} of the expected
absolute error will increase by $\beta_\alpha$. If $\beta_\alpha$ is positive,
it means that the absolute error decreases as the true value of \gls{alpha}
increases.}}

% latex table generated in R 3.2.3 by xtable 1.8-2 package
% Tue May 31 17:03:28 2016
\begin{table}[ht]
\centering
\begin{tabular}{llll}
  \hline
Parameter & Estimate & Standard error & $p$-value \\ 
  \hline
(Intercept) & $2$ & $0.6$ & $0.01$ \\ 
  $\alpha$ & $10$ & $2$ & ${<}10^{-5}$ \\ 
  I & $-3\!\times\!10^{-4}$ & $2\!\times\!10^{-4}$ & $0.7$ \\ 
  m & $0.5$ & $0.2$ & $0.01$ \\ 
   \hline
\end{tabular}
\caption[Parameters of a fitted GLM relating error in estimated $\alpha$ to true values of BA parameters.]{Parameters of a fitted GLM relating error in estimated $\alpha$ to true values of BA parameters. GLM was fitted with a Gaussian distribution and inverse link function. Coefficients are interpretable as additive effects on the inverse of the mean error.} 
\label{tab:glmalpha}
\end{table}
% latex table generated in R 3.2.3 by xtable 1.8-2 package
% Tue May 31 17:03:28 2016
\begin{table}[ht]
\centering
\begin{tabular}{llll}
  \hline
Parameter & Estimate & Standard error & $p$-value \\ 
  \hline
(Intercept) & $0.004$ & $5\!\times\!10^{-4}$ & ${<}10^{-5}$ \\ 
  $\alpha$ & $-0.001$ & $2\!\times\!10^{-4}$ & ${<}10^{-5}$ \\ 
  I & $-4\!\times\!10^{-7}$ & $2\!\times\!10^{-7}$ & $0.05$ \\ 
  m & $-7\!\times\!10^{-5}$ & $8\!\times\!10^{-5}$ & $1$ \\ 
   \hline
\end{tabular}
\caption[Parameters of a fitted GLM relating error in estimated $I$ to true values of BA parameters.]{Parameters of a fitted GLM relating error in estimated $I$ to true values of BA parameters. GLM was fitted with a gaussian distribution and inverse link function. Coefficients are interpretable as additive effects on the inverse of the mean error.} 
\label{tab:glmI}
\end{table}

{\color{blue}\uline{The \gls{GLM} analysis indicated that the error in estimates of
\gls{alpha} decreased with larger true values of \gls{alpha} 
    ($p {<}10^{-5}$)
and \gls{m}
    ($p =0.01$)
but was not significatly affected by \gls{I}} (\cref{tab:glmalpha}). 
\uline{Qualitatively, \gls{alpha} seemed to be only weakly identifiable between
the values of 0 and 0.5} (\cref{fig:abcptm2}). \uline{The error in the
estimated prevalence \gls{I} was slightly lower for smaller values of
\gls{alpha}
    ($p {<}10^{-5}$)
and \gls{I}
    ($p =0.05$),
but was not significantly affected by the true value of \gls{m}} 
(\cref{tab:glmI}).}

@@

%    \input{\tablepath/pa-gamma-glm}
%    \caption{Estimated \gls{GLM} parameters for relationship between power-law
%    exponent \gls{gamma} and \gls{BA} model parameters.}
%    \label{tab:glm}
